Online Verification of Commutativity

### 2020-10-07 acmPaper/paper.tex
ACM stuff

\newcount\draft\draft=0 % set to 0 for submission or publication
% \documentclass[sigplan,review,anonymous]{acmart}
\documentclass[sigplan,review,nonacm=true]{acmart}
\setcopyright{none}
%
\usepackage{tikz}
\usetikzlibrary{snakes}
\usepackage[norelsize]{algorithm2e}
\usepackage{xxx}
\usepackage{fncylab}
\usepackage{subcaption}
\usepackage{listings}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

@@

@@

\begin{document}
\settopmatter{printacmref=false}
\title{Online Verification of Commutativity}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Aditi Kabra \quad Dietrich Geisler \quad Adrian Sampson}
\affiliation{%
  \institution{Cornell University}
}
% ACM publication cruft.
\acmJournal{PACMPL}
\acmVolume{1}
\acmNumber{TAPAS}
\acmArticle{1}
\acmYear{2020}
\acmMonth{1}
\acmDOI{} % \acmDOI{10.1145/nnnnnnn.nnnnnnn}
\startPage{1}

@@

>>>>

\newcount\draft\draft=0 % set to 0 for submission or publication
% \documentclass[sigplan,review,anonymous]{acmart}
% \documentclass[sigplan,nonacm=true]{acmart}
\documentclass[sigplan]{acmart}
\setcopyright{none}
%
\usepackage{tikz}
\usetikzlibrary{snakes}
\usepackage[norelsize]{algorithm2e}
\usepackage{xxx}
\usepackage{fncylab}
\usepackage{subcaption}
\usepackage{listings}
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following line
% to display URLs in blue roman font according to Springer's eBook style:
% \renewcommand\UrlFont{\color{blue}\rmfamily}
\AtBeginDocument{%
  \providecommand\BibTeX{{%
    \normalfont B\kern-0.5em{\scshape i\kern-0.25em b}\kern-0.8em\TeX}}}

@@

%%% The following is specific to TAPAS '20 and the paper
%%% 'Online Verification of Commutativity'
%%% by Aditi Kabra, Dietrich Geisler, and Adrian Sampson.
%%%
\setcopyright{acmlicensed}
\acmPrice{15.00}
\acmDOI{10.1145/3427764.3428322}
\acmYear{2020}
\copyrightyear{2020}
\acmSubmissionID{splashws20tapasmain-id5-p}
\acmISBN{978-1-4503-8189-5/20/11}
\acmConference[TAPAS '20]{Proceedings of the 11th ACM SIGPLAN International Workshop on Tools for Automatic Program Analysis}{November 17, 2020}{Virtual, USA}
\acmBooktitle{Proceedings of the 11th ACM SIGPLAN International Workshop on Tools for Automatic Program Analysis (TAPAS '20), November 17, 2020, Virtual, USA}

\begin{CCSXML}
    <ccs2012>
       <concept>
           <concept_id>10003752.10003766.10003776</concept_id>
           <concept_desc>Theory of computation~Regular languages</concept_desc>
           <concept_significance>500</concept_significance>
           </concept>
       <concept>
           <concept_id>10003752.10003809.10003635.10010038</concept_id>
           <concept_desc>Theory of computation~Dynamic graph algorithms</concept_desc>
           <concept_significance>500</concept_significance>
           </concept>
     </ccs2012>
\end{CCSXML}

\ccsdesc[500]{Theory of computation~Regular languages}
\ccsdesc[500]{Theory of computation~Dynamic graph algorithms}

@@

\begin{document}
\settopmatter{printacmref=false}
\title{Online Verification of Commutativity}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Aditi Kabra \quad Dietrich Geisler \quad Adrian Sampson}
\affiliation{%
  \institution{Cornell University}
}

\startPage{1}

@@

\keywords{commuting diagrams, automatic type conversion, online verification}
